---
title: "Main"
author: "jessica moczulski, Bree Willard, Katie Tong"
date: "2023-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("readr")
install.packages("lubridate")
library(dplyr)
library(tidyr)
library(readr) 
library(lubridate)
library(ggplot2)
```


#loading in air data 
```{r}
neon_air_CPER <- read_csv("../Data/Processed/CPER/NEON_temp-air-single/CPER_Sep_2017_Air_30min/NEON.D10.CPER.DP1.00002.001.000.030.030.SAAT_30min.2017-09.expanded.20221201T015159Z.csv") %>%
  mutate(siteID = "CPER")

neon_air_RMNP <- read_csv("../Data/Processed/RMNP/RMNP/NEON_temp-air-single/RMNP_Sep_2017_Air/NEON.D10.RMNP.DP1.00002.001.000.030.030.SAAT_30min.2017-09.basic.20221210T032125Z.csv") %>%
  mutate(siteID = "RMNP")
```

#mutating the air data by day for both CPER and RMNP
```{r}
neon_air_CPER_DAY <- neon_air_CPER %>%
  mutate(day = floor_date(startDateTime, unit = "day"))

summary(neon_air_CPER_DAY)

```
```{r}
neon_air_RMNP_DAY <- neon_air_RMNP %>%
  mutate(day = floor_date(startDateTime, unit = "day"))

summary(neon_air_RMNP_DAY)
```

#Summary and binding of the columns 
```{r}
neon_air_total <- bind_rows(neon_air_CPER, neon_air_RMNP)

summary(neon_air_total)

```

#Binding the sites 
```{r}
neon_air_total_DAY <- bind_rows(neon_air_CPER_DAY , neon_air_RMNP_DAY)

summary(neon_air_total_DAY)

neon_air_total_DAY <- bind_rows(neon_air_CPER_DAY , neon_air_RMNP_DAY)
```

#loading in soil data for CPER
```{r}
NEON_SOIL_CPER_1 <-read_csv("../Data/Processed/CPER/NEON_heatflux-soil/NEON.D10.CPER.DP1.00040.001.2017-09.expanded.20230127T120753Z.RELEASE-2023/NEON.D10.CPER.DP1.00040.001.001.501.030.SHF_30min.2017-09.expanded.20221201T051650Z.csv")

NEON_SOIL_CPER_2 <-read_csv("../Data/Processed/CPER/NEON_heatflux-soil/NEON.D10.CPER.DP1.00040.001.2017-09.expanded.20230127T120753Z.RELEASE-2023/NEON.D10.CPER.DP1.00040.001.003.501.030.SHF_30min.2017-09.expanded.20221201T051650Z.csv")

NEON_SOIL_CPER_3 <-read_csv("../Data/Processed/CPER/NEON_heatflux-soil/NEON.D10.CPER.DP1.00040.001.2017-09.expanded.20230127T120753Z.RELEASE-2023/NEON.D10.CPER.DP1.00040.001.005.501.030.SHF_30min.2017-09.expanded.20221201T051650Z.csv")

```


#binding rows of soil data 
```{r}

neon_soil_cper_total <- bind_rows(NEON_SOIL_CPER_1, NEON_SOIL_CPER_2, NEON_SOIL_CPER_3)

summary(neon_soil_cper_total)

```


#Mutating binded rows by day and site 
```{r}

neon_SOIL_CPER_TOTAL_DAY <- neon_soil_cper_total %>%
  mutate(day = floor_date(startDateTime, unit = "day")) %>%
  mutate(siteID = "CPER")

summary(neon_SOIL_CPER_TOTAL_DAY)
```


#loading in soil data for RMNP
```{r}
NEON_SOIL_RMNP_1 <-read_csv("../Data/Processed/RMNP/NEON_heatflux-soil/NEON.D10.RMNP.DP1.00040.001.2017-09.basic.20230127T120753Z.RELEASE-2023/NEON.D10.RMNP.DP1.00040.001.001.501.030.SHF_30min.2017-09.basic.20221210T040113Z.csv")

NEON_SOIL_RMNP_2 <-read_csv("../Data/Processed/RMNP/NEON_heatflux-soil/NEON.D10.RMNP.DP1.00040.001.2017-09.basic.20230127T120753Z.RELEASE-2023/NEON.D10.RMNP.DP1.00040.001.003.501.030.SHF_30min.2017-09.basic.20221210T040113Z.csv")

NEON_SOIL_RMNP_3 <-read_csv("../Data/Processed/RMNP/NEON_heatflux-soil/NEON.D10.RMNP.DP1.00040.001.2017-09.basic.20230127T120753Z.RELEASE-2023/NEON.D10.RMNP.DP1.00040.001.005.501.030.SHF_30min.2017-09.basic.20221210T040113Z.csv")
```


#binding rows of soil data and mutating binded rows by day and site
```{r}

neon_soil_RMNP_total <- bind_rows(NEON_SOIL_RMNP_1, NEON_SOIL_RMNP_2, NEON_SOIL_RMNP_3)

summary(neon_soil_RMNP_total)

```
```{r}

neon_SOIL_RMNP_TOTAL_DAY <- neon_soil_RMNP_total %>%
  mutate(day = floor_date(startDateTime, unit = "day")) %>%
  mutate(siteID = "RMNP")

summary(neon_SOIL_RMNP_TOTAL_DAY)
```

# Loading vegetation data for CPER and RMNP
```{r}

Neon_VegCPER_1 <-read_csv("Vegetative_Structure_Code/CPER/Neon_VegCPER_1.csv")  

Neon_VegCPER_2 <-read_csv ("Vegetative_Structure_Code/CPER/Neon_VegCPER_2.csv")

Neon_VegCPER_3 <-read_csv("Vegetative_Structure_Code/CPER/Neon_VegCPER_3.csv")

Neon_VegCPER_4 <-read_csv("Vegetative_Structure_Code/CPER/Neon_VegCPER_4.csv")

Neon_VegCPER_5 <-read_csv("Vegetative_Structure_Code/CPER/Neon_VegCPER_5.csv")

Neon_VegCPER_6 <-read_csv("Vegetative_Structure_Code/CPER/Neon_VegCPER_6.csv")

Neon_VegCPER_7 <-read_csv("Vegetative_Structure_Code/CPER/Neon_VegCPER_7.csv")

Neon_VegCPER_8 <-read_csv("Vegetative_Structure_Code/CPER/Neon_VegCPER_8.csv")

```

```{r}
Neon_VegRMNP_1 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_1.csv") 

Neon_VegRMNP_3 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_3.csv")

Neon_VegRMNP_4 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_4.csv")

Neon_VegRMNP_5 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_5.csv")

Neon_VegRMNP_6 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_6.csv")

Neon_VegRMNP_7 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_7.csv")

Neon_VegRMNP_8 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_8.csv")

Neon_VegRMNP_9 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_9.csv")

Neon_VegRMNP_10 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_10.csv")

Neon_VegRMNP_11 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_11.csv")

Neon_VegRMNP_12 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_12.csv")

Neon_VegRMNP_13 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_13.csv")

Neon_VegRMNP_14 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_14.csv")

Neon_VegRMNP_15 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_15.csv")

Neon_VegRMNP_16 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_16.csv")

Neon_VegRMNP_17 <-read_csv("Vegetative_Structure_Code/RMNP/Neon_VegRMNP_17.csv")

```




#taking the difference of air and soil to get mean temp and summarizing the data 
``` {r}
neon_air_total_DAY %>%
  drop_na(tempSingleMean)%>%
  group_by(siteID, day)%>%
  summarize(mean_temp = mean(tempSingleMean)) -> mean_temp

mean_temp
```
```{r}
neon_soil_total_day <- bind_rows(neon_SOIL_CPER_TOTAL_DAY , neon_SOIL_RMNP_TOTAL_DAY)
```

```{r}
neon_soil_total_day %>%
  drop_na(SHFMean)%>%
  group_by(siteID , day) %>%
  summarize(mean_soil_temp = mean(SHFMean)) -> mean_soil_temp
```

```{r}
neon_difference <- left_join(mean_soil_temp , mean_temp) %>%
  mutate(temp_difference = (mean_temp - mean_soil_temp))

neon_difference
```


```{r}
summary(neon_soil_total_day)
```

<<<<<<< HEAD


#Start of vegetation chunk to produce a visualization 
#Binding rows 

``` {r}
neon_veg_CPER <- bind_rows(Neon_VegCPER_1, Neon_VegCPER_2, Neon_VegCPER_3, Neon_VegCPER_4, Neon_VegCPER_5, Neon_VegCPER_6, Neon_VegCPER_7, Neon_VegCPER_8)
 

summary(neon_veg_CPER)

neon_veg_RMNP <- bind_rows(Neon_VegRMNP_1, Neon_VegRMNP_3, Neon_VegRMNP_4, Neon_VegRMNP_5, Neon_VegRMNP_6, Neon_VegRMNP_7, Neon_VegRMNP_8, Neon_VegRMNP_9, Neon_VegRMNP_10, Neon_VegRMNP_11, Neon_VegRMNP_12, Neon_VegRMNP_13, Neon_VegRMNP_14, Neon_VegRMNP_15, Neon_VegRMNP_16, Neon_VegRMNP_17)


summary(neon_veg_RMNP)



```

#filtering for only 2017
```{r}
Neon_Veg_CPER2017 <- neon_veg_CPER %>% 
  filter(as_date(date) >= as_date("2017-01-01") & 
         as_date(date) <= as_date("2017-12-31"))

summary(Neon_Veg_CPER2017)

Neon_Veg_RMNP2017 <- neon_veg_RMNP %>% 
  filter(as_date(date) >= as_date("2017-01-01") & 
         as_date(date) <= as_date("2017-12-31"))

summary(Neon_Veg_RMNP2017)


```

#Getting summary for the mean max crown diameter at the different plots within the different sites  
```{r}

neon_veg_CPERsummary <- Neon_Veg_CPER2017 %>%
  group_by(plotID, siteID) %>%
  summarize(mean_cover = mean(maxCrownDiameter, na.rm=T)) %>%
  drop_na()

neon_veg_CPERsummary

```

```{r}
neon_veg_RMNPsummary <- Neon_Veg_RMNP2017 %>%
  group_by(plotID, siteID) %>%
  summarize(mean_cover = mean(maxCrownDiameter, na.rm=T)) %>%
  drop_na()

neon_veg_RMNPsummary

```

#Binding the infromation

```{r}
total_veg <- bind_rows(neon_veg_RMNPsummary,neon_veg_CPERsummary)
summary(total_veg)

```


#Second visulization for context on the difference in site composition

```{r}
total_veg%>%
  group_by(siteID)%>%
  summarize(mean_mean_cover = mean(mean_cover, na.rm=T), standard_error = sd (mean_cover, na.rm=T)/sqrt(n())) %>%
  drop_na() %>%
  rename(`Mean Plant Cover`= mean_mean_cover) %>%
  ggplot(aes(x=siteID, y=`Mean Plant Cover`, fill= siteID))+ 
  geom_col()+ 
  geom_errorbar(aes(ymin = `Mean Plant Cover` - standard_error, ymax = `Mean Plant Cover` + standard_error), width = .8)


total_veg


```
#Figure Caption: Figure 2 shows the mean percent cover found within the sites RMNP and CPER. The mean cover recorded includes the max crown diameter of the vegetation found within both sites. 

``` {r} 

model_totalveg <- aov(mean_cover ~siteID, data = total_veg)

summary(model_totalveg)

TukeyHSD(model_Temp_Diff)

```






=======

#Figure 1, this will be our main visualization to test our hypothesis 




```{r}

neon_difference %>%
  group_by(day , siteID) %>%
  ggplot(aes(x = day , y = temp_difference)) +
  geom_point(aes(color = siteID)) +
  geom_line(aes(color = siteID))

```
#Figure Caption: The line plot above describes the relationship between the temperature difference of air and soil between two sites during September 2017.The red lines are RMNP. The blue lines CPER.


#ANOVA analysis for our temperature difference
```{r}

model_Temp_Diff <- aov(temp_difference ~siteID, data = neon_difference)

summary(model_Temp_Diff)

TukeyHSD(model_Temp_Diff)

```
#The ANOVA indicates an F(1,50)=35.85, p< 0.01.This indicates a significant difference between the sites RMNP and CPER's temperature differences. 
 

#Bar graph to accompany the ANOVA analysis and also tests our hypothesis 
```{r}
neon_difference %>%
  drop_na(temp_difference) %>%
  group_by(siteID) %>%
  summarize(mean_temp_difference = mean(temp_difference), standard_error = sd(temp_difference)/sqrt(n())) %>% 
  rename(`Mean Temperature Difference`= mean_temp_difference) %>%
  ggplot(aes(x=siteID , y= `Mean Temperature Difference`))+
  geom_col(aes(color = siteID))+
  geom_errorbar(aes(ymin = `Mean Temperature Difference` - standard_error, ymax = `Mean Temperature Difference` + standard_error), width = .8)
```
#Figure Caption: The figure is a barplot comparing CPER and RMNP temperature difference.  Sites are shown along the x-axis and the average temperature difference is on the y-axis.  There is a clear and large difference between the two with short error bars.



```{r}

plot(model_Temp_Diff)

```


<<<<<<< HEAD
=======

#Histograms for the soil temperature at RMNP and CPER site 

```{r}

neon_SOIL_CPER_TOTAL_DAY %>% 
  group_by(day) %>% 
  summarize(mean_temp = mean(SHFMean)) %>% 
  ggplot(aes(x=mean_temp))+
  geom_histogram()

```

#Figure Caption: The histogram above shows the count of mean Soil Heat Flux per day (Mean_Temp) for the site CPER during September 2017.

```{r}

neon_SOIL_RMNP_TOTAL_DAY %>% 
  group_by(day) %>% 
  summarize(mean_temp = mean(SHFMean)) %>% 
  ggplot(aes(x=mean_temp))+
  geom_histogram()

```

#Figure Caption: The histogram above shows the count of mean Soil Heat Flux per day (Mean_Temp) for the site RMNP during September 2017.
